---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# hJAM

<!-- badges: start -->
<!-- badges: end -->

hJAM is a hierarchical model which unifies the framework of Mendelian Randomization and Transcriptome-wide association studies.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
if (!require("devtools")) { install.packages("devtools") } else {}
devtools::install_github("lailylajiang/hJAM")
```
## Example

This is a basic example of fitting hJAM model:

```{r example}
library(hJAM)
# Download the example data (from simulation) from the package
data(Gl)
data(betas.Gy)
data(conditional_A)
data(marginal_A)
```

If you don't have conditional A matrix, you can use ``get_cond_A`` (if more than one X) or ``get_cond_alpha`` (if only one X) to convert the marginal effects to conditional A matrix with the reference panel.

```{r get_cond}
conditional_A = get_cond_A(marginal_A = marginal_A, Gl = Gl, N.Gx = 1000, ridgeTerm = T)
conditional_alpha = get_cond_alpha(alphas = marginal_A[, 1], Gl = Gl, N.Gx = 1000, ridgeTerm = T)
```

After obtained the conditional A matrix, fit hJAM model with function ``hJAM_lnreg``.

```{r fit_hJAM}
# fit the hJAM model
hJAM_lnreg(betas.Gy = betas.Gy, Gl = Gl, N.Gy = 5000, A = conditional_A, ridgeTerm = T)
```

In the package, you could also implement hJAM with Egger regression, which is designed to detect the unmeasured pleiotropy effect. The function for hJAM with Egger regression is ``hJAM_egger``.

```{r fit_hJAMegger}
# fit the hJAM model
hJAM_egger(betas.Gy = betas.Gy, Gl = Gl, N.Gy = 5000, A = conditional_A, ridgeTerm = T)
```


