---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# JAM: Joint Analysis of Marginal summary statistics

<!-- badges: start -->
[![R build status](https://github.com/lailylajiang/hJAM/workflows/R-CMD-check/badge.svg)](https://github.com/lailylajiang/hJAM)
<!-- badges: end -->

<!-- CRAN badges: start -->
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/hJAM)](https://CRAN.R-project.org/package=hJAM)[![Downloads](http://cranlogs.r-pkg.org/badges/grand-total/hJAM)](https://CRAN.R-project.org/package=hJAM)
<!-- CRAN badges: end -->

## About 

In this package, we provide three `JAM`-family methods that utilize GWAS summary statistics to perform post-GWAS analysis, including Mendelian Randomization, TWAS, and multi-population fine-mapping.  

## hJAM 

hJAM (`hJAM`) is a hierarchical model which unifies the framework of Mendelian Randomization and Transcriptome-wide association studies. The hJAM-Egger (`hJAM_egger`) is a natural extension on hJAM that uses an intercept term to account for the pleiotropy effect of the SNPs on the outcome. 

Additionally, we provide implementations to construct the weight matrix `A` in hJAM. `JAM_A` converts the marginal summary statistics into conditional ones by using the correlation matrix of the SNPs from a reference data. `susieJAM_A` selects SNPs for one intermediate using the marginal summary statistics from GWAS or other study summary data. 

## SHA-JAM
SHA-JAM (`SHAJAM`) is a scalable version of `hJAM` that handles high-dimensional intermediates. SHA-JAM performs model selection from highly correlated intermediates through SuSiE: Sum of Single Effect Model (`SHAJAM`) or elastic-net (`EN.hJAM`). 

## mJAM
mJAM is for multi-population fine-mapping using GWAS summary statistics and credible set construction. We provide two implementations of mJAM: one through SuSiE (`mJAM_SuSiE`) and another one through forward selection (`mJAM_Forward`). `mJAM_Forward` also provides the flexiblity of constructing credible sets for using user-defined index SNPs. A tutorial to get started with mJAM can be found [here](https://jiayi-s.github.io/more_on_mJAM/). 

## Citing this work

* **hJAM**: Jiang, L., Xu, S., Mancuso, N., Newcombe, P. J., & Conti, D. V. (2021). A Hierarchical Approach Using Marginal Summary Statistics for Multiple Intermediates in a Mendelian Randomization or Transcriptome Analysis. *American journal of epidemiology*, 190(6), 1148–1158. https://doi.org/10.1093/aje/kwaa287

* **SHA-JAM**: Jiang, L., Conti, D.V. SHA-JAM: A Scalable Hierarchical Approach to Joint Analysis for Marginal Summary Statistics with Omics Data. (In preparation).

* **mJAM**: Shen, J., Jiang, L., Wang, K., Wang, A., Chen, F., Newcombe, P.J., Haiman, C.A., & Conti, D.V. Fine-Mapping and Credible Set Construction using a Multi-population Joint Analysis of Marginal Summary Statistics from Genome-wide Association Studies.  ([Preprint](https://www.biorxiv.org/content/10.1101/2022.12.22.521659v1) available)


## Quick start with hJAM package

You can install the published version of hJAM from CRAN with:

``` r
install.packages("hJAM")
```

Currently we are working on improving `hJAM` package and adding genome-wide implementation of mJAM. If you want to use the most updated version of this package, we recommend installing the development version from [GitHub](https://github.com/USCbiostats/hJAM) with:

``` r
if (!require("devtools")) { install.packages("devtools") } else {}
devtools::install_github("USCbiostats/hJAM")
```

## Session info

```{r session info}
sessionInfo()
```

